Modular Deep Encoder-Decoders

### 2016-04-28 paper/draft.tex
added core.tex
Added draft of pdf.

\author{Group 40: Arnold, Gurunat, Huang, \& Qu}
\title{Modular Deep Encoder-Decoders}
\date{\today}
\documentclass[12pt]{article}
\usepackage{amsfonts}
%\input{\string~/tex_templates/core}

@@

%\section{Method}\label{method}

\section{Database}\label{materials}

We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

\section{Procedure}\label{procedure}

\subsection{Data Pre-processing and Features}

@@

\subsection{Neural Network Architecture}
\subsubsection{Embedding Layer}
An embedding layer is used to compute a word embedding $W: words \mapsto \mathbb{R}^{n}$ which is a function mapping words of a language to a high dimensional vectors which are continuous, distributed representation of the vocabulary words with good semantic properties. The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.
\subsection{Baseline System}
Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles. Identical architectures are used for both the baseline systems. The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of both the embedding layer and the LSTM was fixed to 128. The output layer is a soft-max layer with 14 dimension for each class representing each journal. Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).

\subsection{Proposed System}
The procedure is quite straight-forward. While part of the team worked
on building our tailored dataset, the other half worked on the model
definition and training procedure.

@@

\subsection{Evaluation Metrics}\label{evaluation}

>>>>

\author{Group 40: Arnold, Gurunat, Huang, \& Qu}
\title{Modular Deep Encoder-Decoders}
\date{\today}
\documentclass[12pt]{article}
\usepackage{amsfonts}
\input{\string./core}

@@

\section{Method}\label{method}
\subsection{Materials}
We used the freely available dataset from
\url{https://github.com/ParallelMazen/SaudiNewsNet} The dataset contains
a total of 31,030 Arabic newspaper articles, with title, author, date,
url and content in each entry. Article objects are reprensented in json
format, with UTF-8 encoding. We wrote a script to download the data from
github repo, unzip each file, and read them in as json objects. The
function can also give out content by key values such as title, author
and etc.

\subsection{Procedure}\label{procedure}

\subsubsection{Data Pre-processing and Features}

@@

%\subsubsection{Neural Network Architecture}
\subsubsection{Embedding Layer}
An embedding layer is used to compute a word embedding $W: words \mapsto \mathbb{R}^{n}$ which is a function mapping words of a language to a high dimensional vectors which are continuous, distributed representation of the vocabulary words with good semantic properties. The hope of such a representation is to project similar words to similar regions in the hyper-space from a semantic point of view.

\subsubsection{Baseline System}
Two baseline systems are constructed, one to classify the journals based on the content of the articles and the second to classify the journals based on the authors of the articles. Identical architectures are used for both the baseline systems. The baseline system is a shallow neural network with one hidden Long Short Term Memory (LSTM) layer succeeding the embedding layer. The dimension of both the embedding layer and the LSTM was fixed to 128. The output layer is a soft-max layer with 14 dimension for each class representing each journal. Cross-Entropy loss function was used as an objective function to train the neural network using Adaptive-Gradient (Adagrad).

\subsubsection{Proposed System}
The procedure is quite straight-forward. While part of the team worked
on building our tailored dataset, the other half worked on the model
definition and training procedure.

@@

\subsection{Evaluation}
